---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# coronavirusupdate

<!-- badges: start -->
<!-- badges: end -->

When the [NDR Coronavirus-Update](https://www.ndr.de/nachrichten/info/podcast4684.html) announced that they would make transcripts of all episodes publicly available I firstly tried to scrape the PDF files, which [kind of worked](https://quickcoffee.netlify.app/post/topic-modelling-on-one-of-germany-s-most-popular-corona-podcast/) but was not very reliable. So I went back and now used the transcripts directly from the [podcast's homepage](https://www.ndr.de/nachrichten/info/Coronavirus-Update-Die-Podcast-Folgen-als-Skript,podcastcoronavirus102.html).  
Consequently I decided to create a R package to make it easy for anyone to scrape and access the data.

## Installation

You can install this package from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("quickcoffee/coronavirusupdate")
```
## Example

This is a basic example how to load the transcript data:

```{r example}
library(coronavirusupdate)
## load data
data("coronavirusupdate_transcripts")
```

This will load a tidy dataframe called `coronavirus_update` with one row per 
paragraph and the following structure:

```{r glimpse, message=FALSE, warning=FALSE}
library(dplyr)
glimpse(coronavirusupdate_transcripts)
```

With this dataset one could for example inspect the share per speaker and 
episode:

```{r pressure, message=FALSE, warning=FALSE}
library(ggplot2)

coronavirusupdate_transcripts %>%
  mutate(paragraph_length = nchar(text)) %>% 
  group_by(episode_no, speaker) %>% 
  summarise(speaker_length = sum(paragraph_length)) %>% 
  group_by(episode_no) %>% 
  mutate(speaker_share = speaker_length/sum(speaker_length)) %>% 
  ggplot(aes(x=episode_no, y=speaker_share, fill = speaker))+
  geom_bar(position="stack", stat="identity")+
  theme_minimal()+
  theme(legend.position="bottom")+
  labs(title = "Share of speaker per episode",
       y = "Share",
       x = "Episode No",
       fill = element_blank())
```
